ms_8

### 2020-04-24 ms_8.Rmd
added comments
joined data

@@

food_access_x <- food_access_x %>% 
    select(State, County, Urban, POP2010, LILATracts_1And10, PovertyRate, MedianFamilyIncome, LA1and10, LAPOP1_10)

food_access_y <- food_access_x %>% 
    rename("state" = State,
           "county" = County,
           "popul" = POP2010,
           "urban" = Urban,
           "lia_1_10" = LILATracts_1And10,
           "poverty" = PovertyRate,
           "med_income" = MedianFamilyIncome,
           "la_1_10" = LA1and10,
           "la_popul" = LAPOP1_10) %>% 
    mutate(urban = as.factor(urban),
           lia_1_10 = as.factor(lia_1_10),
           la_1_10 = as.factor(la_1_10))

@@

# food_lia$perc =  paste(round(100*food_lia$perc, digits = 0), "%", sep="")

food_lia_plot <- food_lia %>% 
    group_by(region) %>% 
    ggplot(aes(x = reorder(state, perc), y = perc, fill = region)) +
    geom_col() +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 65, hjust = 0.3, size = 7),
          panel.grid.major.x = element_line(color = "white"),
          plot.subtitle = element_text(size = 8)) +
    labs(title = "Percent of Counties with a Lack of Food Access",
         subtitle = "Lack of Food Access Defined by 33% of the Population Living More Than \n 1 Mile (Urban) Or 10 Miles (Rural) Away from Supermarket, Supercenter, or Grocery Store",
         caption = "Data from US Department of Agriculture and 2010 Census Bureau",
         x = "State",
         y = "Percent of Counties",
         fill = "Region")

@@

>>>>

# Maybe choose a state to look at its obesity rate change over time

@@

food_access_x <- food_access_x %>% 
    select(State, County, Urban, POP2010, LILATracts_1And10, PovertyRate, MedianFamilyIncome, 
           LA1and10, LAPOP1_10, LALOWI1_10)

food_access_y <- food_access_x %>% 
    rename("state" = State,
           "county" = County,
           "popul" = POP2010,
           "urban" = Urban,
           "poverty" = PovertyRate,
           "med_income" = MedianFamilyIncome,
           "lia_1_10" = LILATracts_1And10,
           "la_1_10" = LA1and10,
           "lia_pop"= LALOWI1_10,
           "la_pop" = LAPOP1_10) %>% 
    mutate(urban = as.factor(urban),
           lia_1_10 = as.factor(lia_1_10),
           la_1_10 = as.factor(la_1_10))

@@

# Maybe could input the region in Shiny and people can play around with that?

food_lia_plot <- food_lia %>% 
    group_by(region) %>% 
    ggplot(aes(y = reorder(state, perc), x = perc, fill = region)) +
    geom_col() +
    theme_minimal() +
    theme(axis.text.y = element_text(hjust = 1, size = 5.5),
          panel.grid.major.y = element_line(color = "white"),
          panel.grid.minor.y = element_line(color = "white"),
          plot.subtitle = element_text(size = 8)) +
    labs(title = "Percent of Counties with a Lack of Food Access and Low Income Population",
         subtitle = "Lack of Food Access Defined by 33% of the Population Living More Than \n 1 Mile (Urban) Or 10 Miles (Rural) Away from Supermarket, Supercenter, or Grocery Store Who are Low Income",
         caption = "Data from US Department of Agriculture and 2010 Census Bureau",
         x = "Percent of Counties",
         y = "State",
         fill = "Region") +
    geom_text(aes(label = perc), hjust = -0.3, size = 2)

@@

```{r join obesity and food access, include=FALSE}

# compare % of people that're obese to % of people that're lia and la

obesity <- obesity %>% 
     mutate(region = case_when(
        state %in% c("CT", "MA", "ME", "NH", "RI", "VT", "NJ", "NY", "PA") ~ "Northeast",
        state %in% c("IL", "IN", "MI", "OH", "WI", "IA", "KS", "MN", "MO", "NE", "ND", "SD") ~ "Midwest",
        state %in% c("DC", "DE", "FL", "GA", "MD", "NC", "SC", "VA", "WV", "AL", "KY", "MS", "TN", "AR", 
                     "LA", "OK", "TX") ~ "South",
        state %in% c("AZ", "CO", "ID", "MT", "NV", "NM", "UT", "WY", "AK", "CA", "HI", "OR", "WA") ~ "West")
    ) %>% 
    mutate(year = as.numeric(year))

obesity_2011 <- obesity %>% 
    filter(year == 2011) %>%
    group_by(state, age, gender, income, race) %>% 
    summarise(mean_perc_obese = round(mean(perc_obese), digits = 0)) %>% 
    filter(state != "US" & state != "DC")

food_sum <- food_access %>% 
    group_by(state, urban) %>% 
    mutate(total_pop = sum(popul),
           total_lia_pop = sum(lia_pop),
           total_la_pop = sum(la_pop),
           perc_lia = round((total_lia_pop/total_pop)*100, digits = 0),
           perc_la = round((total_la_pop/total_pop)*100, digits = 0)) %>% 
    group_by(state, perc_lia, perc_la, urban) %>% 
    summarise(mean_poverty = round(mean(poverty), digits = 0)) %>% 
    filter(!is.na(state))

food_sum <- food_access %>% 
    group_by(state, urban, lia_pop, la_pop, region) %>% 
    summarise(total_pop = sum(popul),
           total_lia_pop = sum(lia_pop),
           total_la_pop = sum(la_pop),
           perc_lia = round((total_lia_pop/total_pop)*100, digits = 0),
           perc_la = round((total_la_pop/total_pop)*100, digits = 0),
           mean_poverty = round(mean(poverty), digits = 0)) %>% 
    select(-total_pop, -total_lia_pop, -total_la_pop, -la_pop, -lia_pop)

joined <- left_join(obesity_2011, food_sum, by = "state")
